---
title: "Linear model"
author: "nz2333"
date: "12/3/2021"
output: html_document
---

```{r}
library(tidyverse)
library(p8105.datasets)

set.seed(1)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


#Import data
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

# Firt a model
```{r}
nyc_airbnb %>%
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()
```

```{r}
fit = lm (price ~ stars +borough, data = nyc_airbnb)
```

Results:
```{r, include = FALSE}
fit

summary(fit)
summary(fit)$coef
coef(fit)
fitted.values(fit)
residuals(fit)
```

look at the results better:
```{r}
broom::glance(fit)

broom::tidy(fit) %>%
  select(-std.error, -statistic) %>%
  mutate(
    term = str_replace(term, "borough", "Borough: ")) %>%
  knitr::kable()
```


## Be in control of factors
```{r}
nyc_airbnb =
  nyc_airbnb %>%
  mutate(
    borough = fct_infreq(borough), 
    room_type = fct_infreq(room_type)
  )

nyc_airbnb %>%
  ggplot(aes(x = stars, y = price, color = borough)) +
  geom_point()

broom::tidy(fit)
```
now the reference group has changed to manhattan. 

## diagnostics
```{r}
nyc_airbnb %>%
modelr::add_residuals(fit) %>%
  ggplot(aes(x = borough, y = resid)) +
  geom_violin() +
  ylim(-500, 1500)

nyc_airbnb %>%
modelr::add_residuals(fit) %>%
  ggplot(aes(x = stars, y = resid)) +
  geom_point() +
  facet_wrap(. ~ borough)

```
added a column in the data frame for residuals based on the model fit. 
From violin plot, can see boroughs with extreme residuals. 
ylim: zoom in the plot

## hypothesis test
```{r}
fit %>%
  broom::tidy()
```
t-test for each parameter, if they are significant

```{r}
fit_null = lm(price ~stars, data = nyc_airbnb)
fit_alt = lm(price ~stars + borough, data = nyc_airbnb)

anova(fit_null, fit_alt) %>%
  broom::tidy()

```

## nest data, fit models
```{r}
fit = lm(price ~ stars * borough + room_type +borough, data = nyc_airbnb) 

broom::tidy(fit)
```

another way, less complex
```{r}
nyc_airbnb %>%
  nest(data = -borough) %>%
  mutate(
    models = map(.x = data, ~lm(price ~ stars, data = .x)),
    results = map(models, broom::tidy)
  ) %>%
  select(-data, -models) %>%
  unnest(results) %>%
  filter(term == "stars")
```
list data for each borough

## nest more
```{r}
nyc_airbnb %>%
  filter(borough == "Manhattan") %>%
  nest(data = -neighborhood) %>%
  mutate(
    models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>%
  select(-data, -models) %>%
  unnest(results) %>%
  filter(str_detect(term, "room_type")) %>%
  ggplot(aes(x = neighborhood, y = estimate)) +
  geom_point() +
  facet_wrap(. ~term)
```














